What the hell is the title of this paper?

### 2018-05-13 NIPS 2018/main.tex
Updates to Sec.3

We consider a distribution $\mathcal{D}$ over tasks, where each task is modeled as a discounted Markov decision process (MDP). We define an MDP as a tuple $\mathcal{M} = \langle \mathcal{S},\mathcal{A},\mathcal{P},\mathcal{R},p_0,\gamma\rangle$, where $\mathcal{S}$ is the state-space, $\mathcal{A}$ is a finite set of actions, $\mathcal{P}(\cdot | s,a)$ is the distribution of the next state $s'$ given that action $a$ is taken in state $s$, $\mathcal{R}: \mathcal{S}\times\mathcal{A}\rightarrow\mathbb{R}$ is the reward function, $p_0$ is the initial-state distribution, and $\gamma\in [0,1)$ is the discount factor. We assume the reward function to be uniformly bounded by a constant $R_{max}>0$. A deterministic policy $\pi : \mathcal{S} \rightarrow \mathcal{A}$ is a mapping from states to actions. At the beginning of each episode of interaction, the initial state $s_0$ is drawn from $p_0$. Then, the agent takes the action $a_0 = \pi(s_0)$, receives a reward $\mathcal{R}(s_0,a_0)$, transitions to the next state $s_1 \sim \mathcal{P}(\cdot | s_0,a_0)$, and the process is repeated. The goal is to find the policy maximizing the long-term return over a possibly infinite horizon: $\max_{\pi}J(\pi)\triangleq\mathbb{E}[\sum_{t=0}^{\infty} \gamma^t r_t \mid \mathcal{M},\pi]$. To this end, we define the optimal value function $Q^*(s,a)$ as the expected return obtained by taking action $a$ in state $s$ and following an optimal policy thereafter. Then, an optimal policy $\pi^*$ is a policy that is greedy with respect to the optimal value function, i.e., $\pi^*(s) = \argmax_a Q^*(s,a)$ for all states $s$. It can be shown (e.g., \cite{puterman1994markov}) that $Q^*$ is the unique fixed-point of the optimal Bellman operator $T$ defined by $TQ(s,a) = \mathcal{R}(s,a) + \gamma\mathbb{E}_{\mathcal{P}}[\max_{a'}Q(s',a')]$ for any value function $Q$. From now on, we adopt the term $Q$-function to denote any plausible value function, i.e., any function $Q : \mathcal{S}\times\mathcal{A} \rightarrow \mathbb{R}$ uniformly bounded by $\frac{R_{max}}{1-\gamma}$.

We consider a parametric family of $Q$-functions, $\mathcal{Q} = \left\{ Q_{\bm{w}} : \mathcal{S}\times\mathcal{A} \rightarrow \mathbb{R} \mid \bm{w}\in\mathbb{R}^K\right\}$ and we assume each function in $\mathcal{Q}$ to be uniformly bounded by $\frac{R_{max}}{1-\gamma}$. When learning the optimal value function, a quantity of interest is how close a given function $Q_{\bm{w}}$ is to the fixed-point of the Bellman operator. A possible measure is its Bellman error (or Bellman residual), defined by $B(\bm{w}) \triangleq TQ_{\bm{w}} - Q_{\bm{w}}$. Notice that $Q_{\bm{w}}$ is optimal if, and only if, $B(\bm{w})(s,a) = 0$ for all $s,a$. If we assume the existence of a distribution $\nu$ over $\mathcal{S}\times\mathcal{A}$, an appealing objective is to directly minimize the squared Bellman error of $Q_{\bm{w}}$ under $\nu$, denoted by $\norm{B(\bm{w})}_{\nu}^2$\todo{Should we define norms before?}. Unfortunately, it is well-known that an unbiased estimator of this quanitity requires two independent samples of the next state $s'$ for each $s,a$ (e.g., \cite{maillard2010finite}). In practice, the Bellman error is typically replaced by the TD error $b(\bm{w})$, which approximates the former using a single transition sample, $b(\bm{w}) = r + \gamma\max_{a'}Q_{\bm{w}}(s',a') - Q_{\bm{w}}(s,a)$. Finally, given a dataset $D = \langle s_i,a_i,r_i,s_i' \rangle_{i=1}^{N}$ of $N$ samples, the squared TD error is computed as $\norm{B(\bm{w})}_{D}^2 = \frac{1}{N}\sum_{i=1}^N (r_i + \gamma \max_{a'} Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i))^2 = \frac{1}{N}\sum_{i=1}^N b_i(\bm{w})^2$. Whenever the distinction is clear from the context, with slight abuse of terminology, we refer to the squared Bellman error and squared TD error as Bellman error and TD error, respectively.

@@

In this section, we describe our variational approach to transfer in RL. In Section \ref{sec:alg}, we start by introducing our algorithm from a high-level perspective, in such a way that it can be used for any choice of prior and posterior distributions. Then, in Sections \ref{sec:gvt} and \ref{sec:mgvt}, we propose practical implementations based on Gaussian prior/posterior and mixture of Gaussian prior/posterior, respectively.

@@

We begin with a simple consideration: the distribution $\mathcal{D}$ over tasks clearly induces a distribution over optimal $Q$-functions. Since, for any MDP, learning its optimal $Q$-function is sufficient for solving the problem, one can safely replace the distribution over tasks with the distribution over their optimal value functions. Furthermore, assume we know such distribution and we are given a new task $\tau$ to solve. Our goal is to design an algorithm that efficiently explores $\tau$ so as to quickly adapt the prior distribution in a Bayesian fashion to put all probability mass over the optimal $Q$-function of $\tau$.

We consider a parametric family of $Q$-functions, $\mathcal{Q} = \left\{ Q_{\bm{w}} : \mathcal{S}\times\mathcal{A} \rightarrow \mathbb{R} \mid \bm{w}\in\mathbb{R}^K\right\}$. For simplicity, we assume each function in $\mathcal{Q}$ to be uniformly bounded by $\frac{R_{max}}{1-\gamma}$\footnote{In practice, this is easily achieved by truncation.}. Then, we can reduce our prior distribution over $Q$-functions to a prior distribution over weights $p(\bm{w})$. Assume that we are given a dataset $D=\left\{(s_i,a_i,s_i',r_i) \mid i = 1,2,\dots N\right\}$ of samples from some task $\tau$ that we want to solve. Then, the posterior distribution over weights given such dataset can be computed by applying Bayes theorem as $p(\bm{w} | D) \propto p(D | \bm{w})p(\bm{w})$. Unfortunately, this cannot be directly used in practice since we do not have a model of the likelihood $p(D|\bm{w})$. In such case, it is very common to make strong assumptions on the MDPs or the $Q$-functions so as to get tractable posteriors \cite{}\todo{Cite somebody}. However, in our transfer settings all distributions involved depend on the family of tasks under consideration, and making such assumptions is likely to limit the applicability of the approach. Thus, we take a different approach to derive a more general and meaningful solution. Recall that our final goal is move all probability mass over the weights minimizing some empirical loss measure, which in our case is the TD error $\norm{B(\bm{w})}_D^2$. Then, given a prior $p(\bm{w})$, we know from PAC-Bayesian theory that the optimal Gibbs posterior takes the form \cite{}\todo{Cite Catoni 2007}:
\begin{equation}\label{eq:gibbs}
q(\bm{w}) = \frac{e^{-\Lambda\norm{B(\bm{w})}_D^2}p(\bm{w})}{\int e^{-\Lambda\norm{B(\bm{w}')}_D^2}p(d\bm{w}')}
\end{equation}
for some parameter $\Lambda > 0$. Since $\Lambda$ is typically chosen to increase with the number of samples $N$, in the remaining we set it to $\lambda^{-1}N$, for some constant $\lambda > 0$. Notice that, whenever the term $e^{-\Lambda\norm{B(\bm{w})}_D^2}$ can be interpreted as the actual likelihood of $D$, $q$ becomes a classic Bayesian posterior. Although we now have an appealing distribution, the integral at the denominator of \eqref{eq:gibbs} is intractable to compute even for simple $Q$-function models. Thus, we propose a variational approximation $q_{\bm{\xi}}$ by considering a simpler family of distributions parameterized by $\bm{\xi} \in \Xi$. Then, our problem reduces to finding the variational parameters $\bm{\xi}$ such that $q_{\bm{\xi}}$ minimizes the Kullback-Leibler (KL) divergence w.r.t. the Gibbs posterior $q$. From the theory of variational inference (e.g., \cite{}\todo{cite}), this can be shown to be equivalent to minimizing the well-known (negative) \textit{evidence lower bound} (ELBO):
\begin{align} \label{eq:elbo}
\min_{\bm{\xi}\in\Xi} \mathcal{L}(\bm{\xi}) = \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[\norm{B(\bm{w})}_D^2\right] - \frac{\lambda}{N}KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right)
\end{align}
Intuitively, the approximate posterior trades-off between placing probability mass over those weights $\bm{w}$ that have low TD error (first term), and staying close to the prior distribution (second term). Assuming that we are able to compute the gradients of \eqref{eq:elbo} w.r.t. the variational parameters $\bm{\xi}$, our objective can be easily optimized with any stochastic optimization algorithm.

@@

We now restrict ourselves to a specific choice of the prior and posterior families that makes our algorithm very efficient and easy to implement. We assume that optimal $Q$-functions according to our task distribution (or better, their weights) follow a multivariate Gaussian law. That is, we model the prior as $p(\bm{w}) = \mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)$ and we learn its parameters from the set of source weights using, e.g., maximum likelihood estimation (with small regularization to make sure the covariance is positive definite). Then, our variational family is the set of all well-defined Gaussian distributions, i.e., the variational parameters are $\Xi = \left\{ (\bm{\mu},\bm{\Sigma}) \mid \bm{\mu}\in\mathbb{R}^K, \bm{\Sigma}\in\mathbb{R}^{K\times K}, \bm{\Sigma}\succ 0 \right\}$. To prevent the covariance from going not positive definite, we consider its Cholesky decomposition $\bm{\Sigma} = \bm{LL}^T$ and learn the lower-triangular Cholesky factor $L$ instead. Under Gaussian distributions, all quantity of interest for using Alg. \ref{alg:transfer} can be computed very easily. The KL divergence between the prior and approximate posterior can be computed in closed-form as:
\begin{equation}
KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right) = \frac{1}{2}\left( \log\frac{\left\lvert \bm{\Sigma}_p \right\rvert}{\left\lvert \bm{\Sigma} \right\rvert} + \text{Tr}\left( \bm{\Sigma}_p^{-1}\bm{\Sigma} \right) + (\bm{\mu} - \bm{\mu}_p)^T \bm{\Sigma}_p^{-1} (\bm{\mu} - \bm{\mu}_p) -K \right)
\end{equation}
for $\bm{\xi} = (\bm{\mu},\bm{L})$ and $\bm{\Sigma} = \bm{LL}^T$. Its gradients with respect to the variational parameters are \cite{}\todo{Cite matrix cookboox}:
\begin{equation}
\nabla_{\bm{\mu}} KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right) = \bm{\Sigma}_p^{-1} (\bm{\mu} - \bm{\mu}_p)
\end{equation}
\begin{equation}
\nabla_{\bm{L}} KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right) = \bm{\Sigma}_p^{-1}\bm{L} - (\bm{L}^{-1})^T
\end{equation}
Finally, the gradients w.r.t. the expected likelihood term of the variational objective \eqref{eq:elbo} can be computed using the reparameterization trick (e.g., \cite{}\todo{Cite deepmind and another}):
\begin{equation}
\nabla_{\bm{\mu}} \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{LL}^T)}\left[ ||B(\bm{w})||_{D}^2 \right] = \mathbb{E}_{\bm{v} \sim \mathcal{N}(\bm{0},\bm{I})}\left[ \nabla_{\bm{w}} ||B(\bm{w})||_{D}^2 \right]\ \ \text{for}\ \ \bm{w} = \bm{Lv} + \bm{\mu}
\end{equation}
\begin{equation}
\nabla_{\bm{L}} \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{LL}^T)}\left[ ||B(\bm{w})||_{D}^2 \right] = \mathbb{E}_{\bm{v} \sim \mathcal{N}(\bm{0},\bm{I})}\left[ \nabla_{\bm{w}} ||B(\bm{w})||_{D}^2 \cdot \bm{v}^T \right]\ \ \text{for}\ \ \bm{w} = \bm{Lv} + \bm{\mu}
\end{equation}

@@

>>>>

We consider a distribution $\mathcal{D}$ over tasks, where each task is modeled as a discounted Markov decision process (MDP). We define an MDP as a tuple $\mathcal{M} = \langle \mathcal{S},\mathcal{A},\mathcal{P},\mathcal{R},p_0,\gamma\rangle$\todo{Should we provide a more transfer-oriented definition?}, where $\mathcal{S}$ is the state-space, $\mathcal{A}$ is a finite set of actions, $\mathcal{P}(\cdot | s,a)$ is the distribution of the next state $s'$ given that action $a$ is taken in state $s$, $\mathcal{R}: \mathcal{S}\times\mathcal{A}\rightarrow\mathbb{R}$ is the reward function, $p_0$ is the initial-state distribution, and $\gamma\in [0,1)$ is the discount factor. We assume the reward function to be uniformly bounded by a constant $R_{max}>0$. A deterministic policy $\pi : \mathcal{S} \rightarrow \mathcal{A}$ is a mapping from states to actions. At the beginning of each episode of interaction, the initial state $s_0$ is drawn from $p_0$. Then, the agent takes the action $a_0 = \pi(s_0)$, receives a reward $\mathcal{R}(s_0,a_0)$, transitions to the next state $s_1 \sim \mathcal{P}(\cdot | s_0,a_0)$, and the process is repeated. The goal is to find the policy maximizing the long-term return over a possibly infinite horizon: $\max_{\pi}J(\pi)\triangleq\mathbb{E}[\sum_{t=0}^{\infty} \gamma^t r_t \mid \mathcal{M},\pi]$. To this end, we define the optimal value function $Q^*(s,a)$ as the expected return obtained by taking action $a$ in state $s$ and following an optimal policy thereafter. Then, an optimal policy $\pi^*$ is a policy that is greedy with respect to the optimal value function, i.e., $\pi^*(s) = \argmax_a Q^*(s,a)$ for all states $s$. It can be shown (e.g., \cite{puterman1994markov}) that $Q^*$ is the unique fixed-point of the optimal Bellman operator $T$ defined by $TQ(s,a) = \mathcal{R}(s,a) + \gamma\mathbb{E}_{\mathcal{P}}[\max_{a'}Q(s',a')]$ for any value function $Q$. From now on, we adopt the term $Q$-function to denote any plausible value function, i.e., any function $Q : \mathcal{S}\times\mathcal{A} \rightarrow \mathbb{R}$ uniformly bounded by $\frac{R_{max}}{1-\gamma}$.

We consider a parametric family of $Q$-functions, $\mathcal{Q} = \left\{ Q_{\bm{w}} : \mathcal{S}\times\mathcal{A} \rightarrow \mathbb{R} \mid \bm{w}\in\mathbb{R}^K\right\}$, and we assume each function in $\mathcal{Q}$ to be uniformly bounded by $\frac{R_{max}}{1-\gamma}$. When learning the optimal value function, a quantity of interest is how close a given function $Q_{\bm{w}}$ is to the fixed-point of the Bellman operator. A possible measure is its Bellman error (or Bellman residual), defined by $B(\bm{w}) \triangleq TQ_{\bm{w}} - Q_{\bm{w}}$. Notice that $Q_{\bm{w}}$ is optimal if, and only if, $B(\bm{w})(s,a) = 0$ for all $s,a$. If we assume the existence of a distribution $\nu$ over $\mathcal{S}\times\mathcal{A}$, an appealing objective is to directly minimize the squared Bellman error of $Q_{\bm{w}}$ under $\nu$, denoted by $\norm{B(\bm{w})}_{\nu}^2$\todo{Should we define norms before?}. Unfortunately, it is well-known that an unbiased estimator of this quanitity requires two independent samples of the next state $s'$ for each $s,a$ (e.g., \cite{maillard2010finite}). In practice, the Bellman error is typically replaced by the TD error $b(\bm{w})$, which approximates the former using a single transition sample, $b(\bm{w}) = r + \gamma\max_{a'}Q_{\bm{w}}(s',a') - Q_{\bm{w}}(s,a)$. Finally, given a dataset $D = \langle s_i,a_i,r_i,s_i' \rangle_{i=1}^{N}$ of $N$ samples, the squared TD error is computed as $\norm{B(\bm{w})}_{D}^2 = \frac{1}{N}\sum_{i=1}^N (r_i + \gamma \max_{a'} Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i))^2 = \frac{1}{N}\sum_{i=1}^N b_i(\bm{w})^2$. Whenever the distinction is clear from the context, with slight abuse of terminology, we refer to the squared Bellman error and squared TD error as Bellman error and TD error, respectively.

@@

In this section, we describe our variational approach to transfer in RL. In Section \ref{sec:alg}, we start by introducing our algorithm from a high-level perspective, in such a way that it can be used for any choice of prior and posterior distributions. Then, in Sections \ref{sec:gvt} and \ref{sec:mgvt}, we propose practical implementations based on Gaussians and mixtures of Gaussians, respectively. We conclude with some considerations on how to optimize the proposed objective in Sec. \ref{sec:td}.

@@

We begin with a simple consideration: the distribution $\mathcal{D}$ over tasks clearly induces a distribution over optimal $Q$-functions. Since, for any MDP, learning its optimal $Q$-function is sufficient for solving the problem, one can safely replace the distribution over tasks with the distribution over their optimal value functions. In particular, we reduce the latter to a distribution $p(\bm{w})$ over weights.

Assume that we are given a dataset $D=\left\{(s_i,a_i,s_i',r_i) \mid i = 1,2,\dots N\right\}$ of samples from some task $\tau$ that we want to solve. Then, the posterior distribution over weights given such dataset can be computed by applying Bayes theorem as $p(\bm{w} | D) \propto p(D | \bm{w})p(\bm{w})$. Unfortunately, this cannot be directly used in practice since we do not have a model of the likelihood $p(D|\bm{w})$. In such case, it is very common to make strong assumptions on the MDPs or the $Q$-functions so as to get tractable posteriors \cite{}\todo{Cite somebody}. However, in our transfer settings all distributions involved depend on the family of tasks under consideration, and making such assumptions is likely to limit the applicability of the approach. Thus, we take a different approach to derive a more general and meaningful solution. Recall that our final goal is move all probability mass over the weights minimizing some empirical loss measure, which in our case is the TD error $\norm{B(\bm{w})}_D^2$. Then, given a prior $p(\bm{w})$, we know from PAC-Bayesian theory that the optimal Gibbs posterior takes the form \cite{}\todo{Cite Catoni 2007}:
\begin{equation}\label{eq:gibbs}
q(\bm{w}) = \frac{e^{-\Lambda\norm{B(\bm{w})}_D^2}p(\bm{w})}{\int e^{-\Lambda\norm{B(\bm{w}')}_D^2}p(d\bm{w}')}
\end{equation}
for some parameter $\Lambda > 0$. Since $\Lambda$ is typically chosen to increase with the number of samples $N$, in the remaining we set it to $\lambda^{-1}N$, for some constant $\lambda > 0$. Notice that, whenever the term $e^{-\Lambda\norm{B(\bm{w})}_D^2}$ can be interpreted as the actual likelihood of $D$, $q$ becomes a classic Bayesian posterior. Although we now have an appealing distribution, the integral at the denominator of \eqref{eq:gibbs} is intractable to compute even for simple $Q$-function models. Thus, we propose a variational approximation $q_{\bm{\xi}}$ by considering a simpler family of distributions parameterized by $\bm{\xi} \in \Xi$. Then, our problem reduces to finding the variational parameters $\bm{\xi}$ such that $q_{\bm{\xi}}$ minimizes the Kullback-Leibler (KL) divergence w.r.t. the Gibbs posterior $q$. From the theory of variational inference (e.g., \cite{}\todo{cite}), this can be shown to be equivalent to minimizing the well-known (negative) \textit{evidence lower bound} (ELBO):
\begin{align} \label{eq:elbo}
\min_{\bm{\xi}\in\Xi} \mathcal{L}(\bm{\xi}) = \mathbb{E}_{\bm{w} \sim q_{\bm{\xi}}}\left[\norm{B(\bm{w})}_D^2\right] - \frac{\lambda}{N}KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right)
\end{align}
Intuitively, the approximate posterior trades-off between placing probability mass over those weights $\bm{w}$ that have low TD error (first term), and staying close to the prior distribution (second term). Assuming that we are able to compute the gradients of \eqref{eq:elbo} w.r.t. the variational parameters $\bm{\xi}$, our objective can be easily optimized with any stochastic optimization algorithm.

@@

We now restrict ourselves to a specific choice of the prior and posterior families that makes our algorithm very efficient and easy to implement. We assume that optimal $Q$-functions according to our task distribution (or better, their weights) follow a multivariate Gaussian law. That is, we model the prior as $p(\bm{w}) = \mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)$ and we learn its parameters from the set of source weights using, e.g., maximum likelihood estimation (with small regularization to make sure the covariance is positive definite). Then, our variational family is the set of all well-defined Gaussian distributions, i.e., the variational parameters are $\Xi = \left\{ (\bm{\mu},\bm{\Sigma}) \mid \bm{\mu}\in\mathbb{R}^K, \bm{\Sigma}\in\mathbb{R}^{K\times K}, \bm{\Sigma}\succ 0 \right\}$. To prevent the covariance from going not positive definite, we consider its Cholesky decomposition $\bm{\Sigma} = \bm{LL}^T$ and learn the lower-triangular Cholesky factor $L$ instead.

@@

Under Gaussian distributions, all quantities of interest for using Alg. \ref{alg:transfer} can be computed very easily. The KL divergence between the prior and approximate posterior can be computed in closed-form as:
\begin{equation}
KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right) = \frac{1}{2}\left( \log\frac{\left\lvert \bm{\Sigma}_p \right\rvert}{\left\lvert \bm{\Sigma} \right\rvert} + \text{Tr}\left( \bm{\Sigma}_p^{-1}\bm{\Sigma} \right) + (\bm{\mu} - \bm{\mu}_p)^T \bm{\Sigma}_p^{-1} (\bm{\mu} - \bm{\mu}_p) -K \right)
\end{equation}
for $\bm{\xi} = (\bm{\mu},\bm{L})$ and $\bm{\Sigma} = \bm{LL}^T$. Its gradients with respect to the variational parameters are \cite{}\todo{Cite matrix cookboox}:
\begin{equation}
\nabla_{\bm{\mu}} KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right) = \bm{\Sigma}_p^{-1} (\bm{\mu} - \bm{\mu}_p)
\end{equation}
\begin{equation}
\nabla_{\bm{L}} KL\left(q_{\bm{\xi}}(\bm{w})\ ||\ p(\bm{w})\right) = \bm{\Sigma}_p^{-1}\bm{L} - (\bm{L}^{-1})^T
\end{equation}
Finally, the gradients w.r.t. the expected likelihood term of the variational objective \eqref{eq:elbo} can be computed using the reparameterization trick (e.g., \cite{}\todo{Cite deepmind and another}):
\begin{equation}
\nabla_{\bm{\mu}} \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{LL}^T)}\left[ ||B(\bm{w})||_{D}^2 \right] = \mathbb{E}_{\bm{v} \sim \mathcal{N}(\bm{0},\bm{I})}\left[ \nabla_{\bm{w}} ||B(\bm{w})||_{D}^2 \right]\ \ \text{for}\ \ \bm{w} = \bm{Lv} + \bm{\mu}
\end{equation}
\begin{equation}
\nabla_{\bm{L}} \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{LL}^T)}\left[ ||B(\bm{w})||_{D}^2 \right] = \mathbb{E}_{\bm{v} \sim \mathcal{N}(\bm{0},\bm{I})}\left[ \nabla_{\bm{w}} ||B(\bm{w})||_{D}^2 \cdot \bm{v}^T \right]\ \ \text{for}\ \ \bm{w} = \bm{Lv} + \bm{\mu}
\end{equation}
